lit

### 2018-08-31 draft.Rmd
abstract finished

This article considers three questions. To what extent does voluntary mobility affect wages; how do internal and external changes compare; and how do institutional contexts foster and hinder the premiums tied to both changes. Results challenge a number of findings in recent literature. First, voluntary mobility is a significant predictor of increased pay, workers who move between and within firms both see a pay related premium after the change. Second, intra-firm career ladders reward workers better than movement between firms in both countries. Last, the effect of intra-firm mobility is larger in Germany than the UK. This suggests British workers must experience several intra-firm changes before seeing substantial gain, while German workers see substantial gain after fewer intra-firm changes. Both countries contain substantial mobility; in both countries firm commitment and career ladders provide the best effect on outcomes. Findings challenge the narrative of mobile and “boundaryless” markets, and question whether mobile markets are inherently “good” for workers.

>>>>

This article compares internal and external mobility in two different institutional contexts. We consider three questions. First, to what extent does voluntary mobility affect earnings growth. Second, how do internal and external mobility types compare in terms of earnings growth. Third, how do mobility types compare in two different institutional settings, Germany and the UK. We offer three findings. First, voluntary mobility has a significant effect on earnings growth, pursuit of quits and promotions is a legitimate strategy for increasing pay. Second, internal career ladders reward workers better than moving between firms. In both countries, promotions and internal movements offer a higher premium to workers than quits and external movements. Three, the effect of promotions is larger in Germany than the UK. This suggests British workers must experience several internal changes before seeing substantial gain, while German workers see substantial gain after fewer internal changes. Workers are mobile in both countries, however, the high premium tied to internal mobility in Germany may act as an incentive to commit to the firm. Findings challenge the narrative of mobile and “boundaryless” markets, and question whether mobile markets are inherently “good” for workers.
